DATA 624 Project 1 Part A - ATM

### 2020-03-24 DATA624/Project 1-A ATM.Rmd
Linted Project 1-A

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(fpp2)
library(forcats)
library(gridExtra)
library(openxlsx)
options(scipen=999)
```

@@

```{r}
if(!file.exists("ATM624Data.xlsx")) {
  download.file("https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA624/ATM624Data.xlsx", "ATM624Data.xlsx")
}

@@

atm %>%
  ggplot(aes(DATE, Cash, color=ATM)) +
  geom_line() +
  ggtitle("Cash Withdrawal by Date and ATM") +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(.~ATM, ncol = 2) +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        axis.title = element_blank())
```

@@

```{r}
atm %>%
  filter(ATM != "ATM4") %>%
  filter(!is.na(ATM)) %>%
  ggplot(aes(DATE, Cash, color=ATM)) +
  geom_line() +
  facet_wrap(.~ATM, ncol = 2) +
  ggtitle("Cash Withdrawal by Date and ATM") +
  scale_color_brewer(palette = "Set1") + 
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        axis.title = element_blank())
```

@@

```{r}
atm %>%
  na.omit() %>%
  mutate(`Day of Week` = recode(as.factor(wday(DATE)), "1" = "Sunday", "2" = "Monday", "3" = "Tuesday", "4"="Wednesday", "5"="Thursday", "6"="Friday","7"="Saturday"))  %>%
  ggplot(aes(`Day of Week`, Cash, color = `Day of Week`)) +
  geom_boxplot() +
  facet_grid(ATM ~ `Day of Week`, scales = "free") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none", axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks = element_blank())
```

@@

```{r}
h <- 31
atm1_stl_ets_fit <- atm1_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="ets")
checkresiduals(atm1_stl_ets_fit)
```

@@

```{r}
atm1_stl_arima_fit <- atm1_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="arima") 
checkresiduals(atm1_stl_arima_fit)
```

@@

stl_ets_errors <- tsCV(atm1_ts, stlf, h = h, s.window = 7, robust = TRUE, method="ets")
stl_arima_errors <- tsCV(atm1_ts, stlf, h = h, s.window = 7, robust = TRUE, method="arima")
hw_errors <- tsCV(atm1_ts, hw, h = h)
adj_hw_errors <- tsCV(atm1_ts, hw, h = h, lambda = atm1_lambda)
arima_errors <- tsCV(atm1_ts, atm1_arima_forecast, h = h)

@@

```{r}
atm2_stl_ets_fit <- atm2_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="ets")
checkresiduals(atm2_stl_ets_fit)
```

@@

```{r}
atm2_stl_arima_fit <- atm2_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="arima") 
checkresiduals(atm2_stl_arima_fit)
```

@@

stl_ets_errors <- tsCV(atm2_ts, stlf, h = h, s.window = 7, robust = TRUE, method="ets")
stl_arima_errors <- tsCV(atm2_ts, stlf, h = h, s.window = 7, robust = TRUE, method="arima")
hw_errors <- tsCV(atm2_ts, hw, h = h)
adj_hw_errors <- tsCV(atm2_ts, hw, h = h, lambda = atm2_lambda)
arima_errors <- tsCV(atm2_ts, atm2_arima_forecast, h = h)

@@

```{r}
atm %>%
  filter(ATM == "ATM3") %>%
  mutate(nonzero = if_else(Cash == 0, "No", "Yes")) %>%
  ggplot(aes(DATE, Cash, color=nonzero)) +
  geom_point() +
  ggtitle("ATM #3") +
  scale_color_brewer(palette = "Set1") +
  theme(axis.title = element_blank(), legend.position = "none")
```

@@

```{r}
atm4_stl_ets_fit <- atm4_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="ets")
checkresiduals(atm4_stl_ets_fit)
```

@@

```{r}
atm4_stl_arima_fit <- atm4_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method="arima") 
checkresiduals(atm4_stl_arima_fit)
```

@@

stl_ets_errors <- tsCV(atm4_ts, stlf, h = h, s.window = 7, robust = TRUE, method="ets")
stl_arima_errors <- tsCV(atm4_ts, stlf, h = h, s.window = 7, robust = TRUE, method="arima")
hw_errors <- tsCV(atm4_ts, hw, h = h)
adj_hw_errors <- tsCV(atm4_ts, hw, h = h, lambda = atm4_lambda)
arima_errors <- tsCV(atm4_ts, atm4_arima_forecast, h = h)

@@

```{r, echo=FALSE}
dates <- seq(ymd('2010-05-01'), ymd('2010-05-31'), by = "1 day")

atm1_forecast <- forecast(atm1_arima_fit, h=h)
atm2_forecast <- forecast(atm2_arima_fit, h=h)
atm3_forecast <- rep(atm3_mean, h)
atm4_forecast <- forecast(atm4_arima_fit, h=h)

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, message = FALSE, warning = FALSE)
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(fpp2)
library(forcats)
library(gridExtra)
library(openxlsx)
options(scipen = 999)
```

@@

```{r}
if (!file.exists("ATM624Data.xlsx")) {
  download.file("https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA624/ATM624Data.xlsx", "ATM624Data.xlsx")
}

@@

atm %>%
  ggplot(aes(DATE, Cash, color = ATM)) +
  geom_line() +
  ggtitle("Cash Withdrawal by Date and ATM") +
  scale_color_brewer(palette = "Set1") +
  facet_wrap(.~ATM, ncol = 2) +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        axis.title = element_blank())
```

@@

```{r}
atm %>%
  filter(ATM != "ATM4") %>%
  filter(!is.na(ATM)) %>%
  ggplot(aes(DATE, Cash, color = ATM)) +
  geom_line() +
  facet_wrap(.~ATM, ncol = 2) +
  ggtitle("Cash Withdrawal by Date and ATM") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        axis.title = element_blank())
```

@@

```{r}
atm %>%
  na.omit() %>%
  mutate(`Day of Week` = recode(as.factor(wday(DATE)), "1" = "Sunday", "2" = "Monday", "3" = "Tuesday", "4" = "Wednesday", "5" = "Thursday", "6" = "Friday", "7" = "Saturday"))  %>%
  ggplot(aes(`Day of Week`, Cash, color = `Day of Week`)) +
  geom_boxplot() +
  facet_grid(ATM ~ `Day of Week`, scales = "free") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none", axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks = element_blank())
```

@@

```{r}
h <- 31
atm1_stl_ets_fit <- atm1_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method = "ets")
checkresiduals(atm1_stl_ets_fit)
```

@@

```{r}
atm1_stl_arima_fit <- atm1_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method = "arima")
checkresiduals(atm1_stl_arima_fit)
```

@@

stl_ets_errors <- tsCV(atm1_ts, stlf, h = h, s.window = 7, robust = TRUE, method = "ets")
stl_arima_errors <- tsCV(atm1_ts, stlf, h = h, s.window = 7, robust = TRUE, method = "arima")
hw_errors <- tsCV(atm1_ts, hw, h = h)
adj_hw_errors <- tsCV(atm1_ts, hw, h = h, lambda = atm1_lambda)
arima_errors <- tsCV(atm1_ts, atm1_arima_forecast, h = h)

@@

```{r}
atm2_stl_ets_fit <- atm2_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method = "ets")
checkresiduals(atm2_stl_ets_fit)
```

@@

```{r}
atm2_stl_arima_fit <- atm2_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method = "arima")
checkresiduals(atm2_stl_arima_fit)
```

@@

stl_ets_errors <- tsCV(atm2_ts, stlf, h = h, s.window = 7, robust = TRUE, method = "ets")
stl_arima_errors <- tsCV(atm2_ts, stlf, h = h, s.window = 7, robust = TRUE, method = "arima")
hw_errors <- tsCV(atm2_ts, hw, h = h)
adj_hw_errors <- tsCV(atm2_ts, hw, h = h, lambda = atm2_lambda)
arima_errors <- tsCV(atm2_ts, atm2_arima_forecast, h = h)

@@

```{r}
atm %>%
  filter(ATM == "ATM3") %>%
  mutate(nonzero = if_else(Cash == 0, "No", "Yes")) %>%
  ggplot(aes(DATE, Cash, color = nonzero)) +
  geom_point() +
  ggtitle("ATM #3") +
  scale_color_brewer(palette = "Set1") +
  theme(axis.title = element_blank(), legend.position = "none")
```

@@

```{r}
atm4_stl_ets_fit <- atm4_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method = "ets")
checkresiduals(atm4_stl_ets_fit)
```

@@

```{r}
atm4_stl_arima_fit <- atm4_ts %>%
  stlf(h = h, s.window = 7, robust = TRUE, method = "arima")
checkresiduals(atm4_stl_arima_fit)
```

@@

stl_ets_errors <- tsCV(atm4_ts, stlf, h = h, s.window = 7, robust = TRUE, method = "ets")
stl_arima_errors <- tsCV(atm4_ts, stlf, h = h, s.window = 7, robust = TRUE, method = "arima")
hw_errors <- tsCV(atm4_ts, hw, h = h)
adj_hw_errors <- tsCV(atm4_ts, hw, h = h, lambda = atm4_lambda)
arima_errors <- tsCV(atm4_ts, atm4_arima_forecast, h = h)

@@

```{r, echo=FALSE}
dates <- seq(ymd("2010-05-01"), ymd("2010-05-31"), by = "1 day")

atm1_forecast <- forecast(atm1_arima_fit, h = h)
atm2_forecast <- forecast(atm2_arima_fit, h = h)
atm3_forecast <- rep(atm3_mean, h)
atm4_forecast <- forecast(atm4_arima_fit, h = h)
